\section{Preparation}\label{i.-preparation}

This section contains the mechanical assembly on the field for the first flight. After this, the system can be turned on for a flight.

\subsubsection*{Pre-assembly check}\label{pre-assembly-check}

      \begin{todolist}
      \item Remove all the nacelle and the fuselage covers.
      \item Attach the \textbf{Remove Before Flight (RBF)} jumpers to the back of
        the aircraft.
      \item Check the \textbf{X} shaped wooden bracer in the middle of the
        fuselage.

        \begin{itemize}
        \itemsep1pt\parskip0pt\parsep0pt
        \item   It should be screwed tightly at 4 points to the fuselage
        \end{itemize}
        \item
          Put on the airscrews with the wrench (size: 14)
      \end{todolist}

\subsubsection*{Sindy wing attaching procedure:}\label{sindy-wing-attaching-procedure}

      Install the wing one-by-one, following these steps:

      \begin{todolist}
      \itemsep1pt\parskip0pt\parsep0pt
      \item Remove the safety screw from the flap shaft and the bolts from the
        side of the wings

        \begin{itemize}
        \itemsep1pt\parskip0pt\parsep0pt
        \item   Put these three screws into the small box, so you could reach them
          easily
        \item   Insert the flap shaft ball bearings from the box and fix the shaft
          in place in the nacelle
        \end{itemize}
      \item Apply the wing to the nacelle

        \begin{itemize}
        \itemsep1pt\parskip0pt\parsep0pt
        \item   Watch out for the cables
        \item   Take care of the joint of flap rotation shaft!
        \end{itemize}
      \item Apply the wooden bracing sticks (to avoid vertical backlash)
      \item Screw in the 2 bolts but do not tighten them
      \item Screw in the wing flap bolt - use the PH-1 screwdriver
      \item Put the small box back to the toolset
      \item Plug the connectors together:

        \begin{itemize}
          \itemsep1pt\parskip0pt\parsep0pt
          \item Servo power supply cables with markings: left side number 2, on
            right side number 8
          \item CAN bus (6-pin white Molex connector)
        \end{itemize}
      \item Tighten the bolt screws a bit with the 5mm Allen wrench
      \end{todolist}

\subsubsection*{Battery check and placement}\label{battery-check-and-placement}

      \begin{todolist}
        \item Check that both \textbf{two} of the RBF jumpers with the red
          \emph{remove before flight} flags are in place - they should be
          \textbf{still attached} to the BECs
        \item Check both circuit breaker plugs of the engine batteries on the side
          of the nacelles - they should be \textbf{disconnected} (unplugged)
          
	 \end{todolist}
     \begin{itemize}
        \item Apply a LiPo alarm device to each battery and check the voltage level
          of each batteries, but do not insert them yet to the aircraft
        
        \begin{todolist}
        	\item Fill the table with the battery values        	
        \end{todolist}
        
%        \begin{itemize}
%          \itemsep1pt\parskip0pt\parsep0pt
%          \item
%            If the voltage level of the \textbf{2S} batteries (2 pieces) for the
%            servos are below \textbf{8.0V} then do not use them. (two needed)
%          \item
%            If the voltage level of the \textbf{2S} batteries (2 pieces) for the
%            RX-MUX units are below \textbf{7.5V} then do not use them. (two
%            needed)
%          \item
%            If the voltage level of the \textbf{6S} battery (2 pieces) for the
%            motors are below \textbf{24.5V} then do not use them. (two needed)
%          \item
%            If the voltage level of the \textbf{6S} battery (1 piece) for the
%            flightHAT is below \textbf{22.0V} then do not use them. (one needed)
%        \end{itemize}

        \begin{table}
        		\centering
        		\caption*{Voltage of the inserted LiPo batteries}
        		\renewcommand{\arraystretch}{2} % to increase cell height
        		\begin{tabular}{|p{1.3cm}|p{2.2cm}|p{1.2cm}|c|p{1.8cm}|p{1.8cm}|p{1cm}|p{1.8cm}|p{1.8cm}|}
        			%\hline
        			%		\begin{tabular}{c|c}
        			%			a  & b \\
        			%			c  & d \\
        			%		\end{tabular} & e  & x & f \\
        			\multicolumn{9}{l}{Batteries for 10 minutes of flight - replace needed between two flight} \\ \hline
        			
        			% column names
        			Connector labels 	&
        			Powered device 		&
        			Min. voltage		&
        				% tricky joined names
        			{Label} & \multicolumn{2}{c|}{\makecell{Voltage at first flight \\ \vspace{-8pt}before~~~~~~~~~~ after}} &
        			{Label} & \multicolumn{2}{c|}{\makecell{Voltage at second flight \\ \vspace{-8pt}before~~~~~~~~~~ after}}
        			\\	\hline

        			% list of batteries
        			6S\_L & ECU & 24.5V &&&&&&  \\
        			\hline
        			6S\_R & ECU & 24.5V &&&&&& \\
        			\hline
        			2S\_L & servo left & 8.0V &&&&&& \\
        			\hline
        			2S\_R & servo right & 8.0V &&&&&&  \\
        			\hline
        			
        			%space
        			\multicolumn{9}{l}{} \\   
        			
        			%whole table wide header     			
        			\multicolumn{9}{l}{Batteries for 20 minutes of flight - no replace needed, just log the voltages after first flight} \\
					\cline{1-6}\cline{9-0}
        			6S\_fH & flightHAT & 22.0V &&&&\multicolumn{2}{l|}{}& \\
					\cline{1-6}\cline{9-9}
        			2S1 & RX-MUX left & 7.5V   &&&&\multicolumn{2}{l|}{}& \\
					\cline{1-6}\cline{9-9}
					2S2 & RX-MUX right & 7.5V  &&&&\multicolumn{2}{l|}{}& \\
					\cline{1-6}\cline{9-9}
        		\end{tabular}
        	\end{table}

      \item
        Fix the batteries to their respective places, but \textbf{DO NOT
        CONNECT THEM YET!}

		  \begin{todolist}
	  
	
	        \itemsep1pt\parskip0pt\parsep0pt
	        \item
	          2 pieces of \textbf{2S} to the back of the main fuselage (servos)
	        \item
	          2 pieces of \textbf{2S} to the front of the main fuselage (RX-MUX)
	        \item
	          1 piece of \textbf{6S} to the front of the main fuselage (flightHAT
	          and sensors)
	        \item
	          1 piece of \textbf{6S} to each engine nacelle (ESCs)
	      \end{todolist}            
	  \end{itemize}      

      \begin{todolist}
        \itemsep1pt\parskip0pt\parsep0pt
        \item
          Make sure that the inline circuit breaker is open on the side of the
          nacelles.
        \item
          Connect the \textbf{6S} batteries to the ESC and put on
          the top casing of the engine nacelles.

          At this time, just this 2
          batteries are plugged in, but the whole system is unpowered, no live
          electrical components present (except LiPo guards).


        \item
          Check the \textbf{CG} - Center of Gravity - of the aircraft. See
          \emph{Appendix}
      \end{todolist}

      The system is now ready to turn on.

\begin{center}\rule{3in}{0.4pt}\end{center}
