	\section{Turn on sequence}\label{ii.-turn-on-sequence}
	
	If one of the following steps are ambiguous or the function does not
	work properly, \textbf{STOP} the process, and do not attempt to fly with
	the system.
	
	\begin{todolist}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  Turn on the JETI transmitter and select the proper flight model -
	  \textbf{Sindy-Flight} for the Sindy aircraft
	
	  \begin{itemize}
	  \itemsep1pt\parskip0pt\parsep0pt
	  \item
	    Check every control switch on the transmitter, and set them to the
	    \textbf{default position}. See \emph{Appendix}
	  \end{itemize}
	\item
	  Powering the \emph{RX-MUX} units
	
	  \begin{itemize}
	  \itemsep1pt\parskip0pt\parsep0pt
	  \item
	    plug in the 2 pieces of \textbf{2S} battery at front of the fuselage
	    according to the labeling
	  \end{itemize}
	\item
	  Checking that the RX-MUX is working (RC communication)
	
	  \begin{itemize}
	  \itemsep1pt\parskip0pt\parsep0pt
	  \item
	    Connection is indicated on DC-24's screen upper left corner: two
	    green \emph{tick}s are present if radio connection is established.
	  \item
	    Search the two red LED indicators on RX-MUX (at the top of the FCC
	    case, left and right side). The RX-MUX for the left and the right
	    side works separately and independently. Now turn on and off the
	    autopilot with the labeled arm and check the LEDs.
	  \item
	    If the red LEDs on the RX-MUX units are turning off and then back
	    again indicating Autopilot state, then you can move to the next
	    step. Leave the transmitter in \textbf{manual flight mode/autopilot
	    off}. See \emph{Appendix}.
	  \end{itemize}
	\item
	  Powering the \emph{servos}
	
	  \begin{itemize}
	  \itemsep1pt\parskip0pt\parsep0pt
	  \item
	    Connect the servo batteries to their respective cables: 2 pieces of
	    \textbf{2S} battery at the back of the fuselage according to the
	    labeling
	  \item
	    Remove the RBF jumpers at the back of the fuselage
	  \item
	    Put the RBF jumpers into the toolkit
	  \item
	    If the main receiver (fuselage front), the satellite receiver (RSAT,
	    at fuselage back) and the RX-MUX are connected and the transmitter
	    is turned on, the servos are about to start working now.
	  \item
	    Check that every control surface deflects in the right direction, by
	    controlling the aircraft with the transmitter.
	  \end{itemize}
	\item
	  Powering the \emph{flightHAT}
	
	  \begin{itemize}
	  \itemsep1pt\parskip0pt\parsep0pt
	  \item
	    Connect the \textbf{6S} battery at front of the fuselage (for
	    flightHAT)
	  \item
	    Wait until the Pi boots up - it may take a minute
	  \item
	    \textbf{Connect to the RaspberryPI} and start the SW\_PI software.
	    For details see \emph{Appendix}
	  \item
	    The software was started at: (table necess.)
	  \end{itemize}
	\item
	  Fire up both the Ground Control Station and the EDL system and check
	  the connection and the received data on both interface
	\item
	  Put on the top casing of the main fuselage
	\item
	  Just before the actual flight, remove the protective cap from the
	  aeroprobe
	\item
	  Put the throttle stick of the transmitter to the middle state
	\item
	  Fix the aircraft - at least one man should hold it on the ground from
	  behind
	\item
	  Connect the two halves of the inline circuit breaker at each nacelle
	  (with caution!), and wait for the beeping sounds
	\item
	  Set the throttle stick to the lowest position. At this point, the
	  throttle is armed, \textbf{stay clear of the airscrews} for safety
	  reasons!
	\item
	  The aircraft is ready for takeoff
	\end{todolist}

	\begin{table}[H]
		\centering
		\caption*{Time of the flight events}
		\renewcommand{\arraystretch}{2} % to increase cell height
		\begin{tabular}{|c|p{2cm}|c|}
			\hline
			
			% header
			\multirow{2}{*}
			{Event} & \multicolumn{2}{c|}{Time} \\	\cline{2-3}
			& First flight & Second flight\\ \hline

			% entries - event names aligned left with multicolumn
			\multicolumn{1}{|l|}{flightHAT turned on} 	& & \\ \hline

			\multicolumn{1}{|l|}{Takeoff} 				& & \\ \hline

			\multicolumn{1}{|l|}{Landing} 				& & \\ \hline

			\multicolumn{1}{|l|}{Logfile No.} 			& & \\ \hline

		\end{tabular}
	\end{table}

%	\begin{center}\rule{3in}{0.4pt}\end{center}
	
